Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-03-27 main.Rmd
labels a, b and c in plots no parenthesis

gg_fig <- ggarrange(scene3, 
          ggarrange(scene1, scene2, ncol = 2, labels = c("(b)", "(c)")),
          nrow = 2, labels = "(a)")
          #label.y = "electricity demand [KWh]"\

@@

gg_fig <- ggarrange(cust2_box, 
          ggarrange(cust2_quantile, cust2_violin, nrow = 2, labels = c("(b)", "(c)")),
          ncol = 2, labels = "(a)")
          #label.y = "electricity demand [KWh]"\

@@

cricket_tsibble %>%
  filter(batting_team %in% c(
    "Mumbai Indians",
    "Chennai Super Kings"
  )) %>%
  mutate(inning = paste0("inning:", inning)) %>% 
  prob_plot("inning",
    "over",
    response = "runs_per_over",
    hierarchy_model,
    plot_type = "lv"
  ) + 
  scale_fill_brewer(palette = "Dark2") + 
  ggtitle("(a) Runs per over across over faceted by inning") +
  theme(legend.position = "right") +
  ggtitle("(a)") +
  ylab("runs per over") +
  xlab("overs of the innings") 
  # ggplot2::theme(
  #     strip.text = ggplot2::element_text(
  #       size = 7,
  #       margin = ggplot2::margin()
  #     )
  #   ) 
  #

@@

# filter(fielding_wckts %in% c(0,1)) %>%
# 
 cricket_data %>%
  filter(over!=1) %>% 
  prob_plot("over", "lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "boxplot",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)
) + ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") + 
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("(b)")
# + geom_boxplot(width = 0.5, aes(colour = lag_field)) 
```

>>>>

gg_fig <- ggarrange(scene3, 
          ggarrange(scene1, scene2, ncol = 2, labels = c("b", "c")),
          nrow = 2, labels = "a")
          #label.y = "electricity demand [KWh]"\

@@

gg_fig <- ggarrange(cust2_box, 
          ggarrange(cust2_quantile, cust2_violin, nrow = 2, labels = c("b", "c")),
          ncol = 2, labels = "a")
          #label.y = "electricity demand [KWh]"\

@@

cricket_tsibble %>%
  filter(batting_team %in% c(
    "Mumbai Indians",
    "Chennai Super Kings"
  )) %>%
  mutate(inning = paste0("inning:", inning)) %>% 
  prob_plot("inning",
    "over",
    response = "runs_per_over",
    hierarchy_model,
    plot_type = "lv"
  ) + 
  scale_fill_brewer(palette = "Dark2") + 
  #ggtitle("(a) Runs per over across over faceted by inning") +
  theme(legend.position = "right") +
  ggtitle("a") +
  ylab("runs per over") +
  xlab("overs of the innings") +
  theme(plot.title = element_text(face = "bold"))
  # ggplot2::theme(
  #     strip.text = ggplot2::element_text(
  #       size = 7,
  #       margin = ggplot2::margin()
  #     )
  #   ) 
  #

@@

# filter(fielding_wckts %in% c(0,1)) %>%
# 
 cricket_data %>%
  filter(over!=1) %>% 
  prob_plot("over", "lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "boxplot",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)) +
   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") + 
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("b") +
   theme(plot.title = element_text(face = "bold"))
# + geom_boxplot(width = 0.5, aes(colour = lag_field)) 
```
